Viral Sequence Sorting Tools Evaluation

### 2022-12-04 TestingPipeline/Scripts/rule_tuning_2022.09.06.Rmd
Testing rule set based on VS2 SOP.

>>>>

viruses_long_scores <- viruses %>% 
  select(contains("keep_score_vb"), true_virus) %>%
  pivot_longer(cols=contains("keep_score_"), 
               names_to="rule_combination",
               values_to="viral_score") %>% 
  mutate(viral_score=as.factor(round(viral_score))) %>%
  group_by(rule_combination, viral_score,true_virus) %>%
  summarise(n = n())
```
